As per topic number DTRA192-003 under the DTRA component, the goal of this proposal is to build computing infrastructure
that utilizes quantum-resistant blockchain frameworks to support Continuity of Operations (COOP) as given in
\cite{whitworth2006}. The specific goal of this project is to support mission critical operation for the Department of
Defense and preserve mission-critical enterprise data during a catastrophic physical attack on the United States. The
technologies and solutions built here can be widely applied to other agency operations as well under the Federal
umbrella. 

Our goal is to build a blockchain-based technology that can survive coordinated attacks and failures such as when
hit by catastrophic nuclear, electromagnetic pulse (EMP), and/or cyberwarfare attacks. The specific goal of this project
is to research, design and implement quantum-crytography based blockchain methods to preserve mission-critical
information. The lessons learned from this project shall further the state of the art in this area which might become
broadly applicable to other failure or disaster scenarios as well (or applicable to other Federal agencies).

The rest of this proposal is organized as follows. In the next Section \ref{sec:overview}, we present a high-level
background of the concepts in blockchain technology and how they might apply for our goal. In Section \ref{sec:design},
we present a design of our blockchain system to fulfill requirements of Phase I and II. Next, in Section \ref{sec:plan},
we present a work plan for Phase I. In Section \ref{sec:related}, we discuss related research in the field that we can
are able to build upon. In Section \ref{sec:pers}, we present our core team that would spend time on this project.

