\label{sec:pers}
In this section, we present technical calibre of the key personnel on the team for this project. The team comprises of
three experts in the field, with the credentials as below:

\subsection*{Dr. Arunesh Mishra}

Dr. Mishra is the Principal on this proposal. He would be spending 70-80\% of his time on this project for its duration.
Dr. Mishra has experience with launching four different product teams during his 10 year tenure at Google. He has built
a planet-wide scalable real-time user location infrastructure that powers 2.5 Billion users's queries every single day.
This system supports real-time traffic, weather, Google searches to name a few products. He holds over 20 granted
patents today with another 15 pending. 

He has a Postdoc in Distributed systems and a PhD in Networking and Security. He has best paper awards in top ACM
conferences. He also started an opensource implementation of the networking security standing given by IEEE 802.1x
(hosted at open1x.org) which is now default in Linux distributions. He is the Founder at Picolo Labs which is building a
blockchain based decentralized database technology.

\subsection*{Rajendra Kumar}

Rajendra Kumar has about 10 years of experienc in building network stack technologies for both wireless and wired
computing. The systems he has designed have been in production use for the last decade. He has implemented various
networking and security protocols for IEEE 802.11, 802.11(ac/b) networks. His experience is highly valuable in designing
a robust, secure, delay-tolerant network stack for the blockchain system.

\subsection*{Dr. Shiva Kintali:} 
Dr. Shiva Kintali is a Founder and CEO of True Group Inc. He is a Mathematician, a Cryptographer, Ex-Princeton Lecturer, Advisor,
Investor and a Public Speaker. He was a Professor of Computer Science at Princeton University for 5 years and has
numerous reputed publications. He is currently
residing in Silicon Valley, working on cutting-edge blockchain technologies. Dr. Kintali is available to work as a
consultant for our project.

\subsection*{Access to talent in Silicon Valley:}
Beyond the core team above, one advantage of our company is its access to talent in the Silicon Valley. In our
immediate profressional network, we have access to more than 20-40 professionals who are available to consult or work on
this project. Also, we have graduates, postdocs and  interns from reputed univesities closeby such as Stanford
University, University of California Berkeley and their professors who we have been in touch through professional
workshops, conferences and meetups.
